\LARGE Performance Evaluation of Xenomai 3

### 2015-10-20 paper.tex
improve multiple author list

\documentclass[10pt,a4paper]{article}
\usepackage[english]{babel}
\usepackage{multicol}
\usepackage{multirow}
\usepackage{url,hyperref,graphicx,float,times}
\usepackage{sectsty}

@@

\author{\large
{\bf Ching-Chun (Jim) Huang, Che-Kang Wu }\\
Department of Computer Science and Information Engineering, \\
National Cheng Kung University, Taiwan\\
No.1, University Road, Tainan City 701, Taiwan (R.O.C.)\\
\vspace{8mm}
jserv$@$ccns.ncku.edu.tw, an4006048$@$mail.ncku.edu.tw\\
{\bf Chan-Hsiang Lin}\\
Department of Electrical and Electronic Engineering, National Taiwan University\\
No.1, Sec. 4, Roosevelt Road, Taipei, Taiwan (R.O.C.)\\
\vspace{8mm}
r04943031$@$ntu.edu.tw\\
}
\date{}

>>>>

\documentclass[10pt,a4paper]{article}
\usepackage[english]{babel}
\usepackage{multicol}
\usepackage{multirow}
\usepackage{url,hyperref,graphicx,float,times}
\usepackage{sectsty}
\usepackage{authblk}

@@

\author[*]{\large
{\bf Ching-Chun (Jim) Huang}\thanks{jserv@ccns.ncku.edu.tw}}
\author[*]{\large
{\bf Che-Kang Wu}\thanks{an4006048$@$mail.ncku.edu.tw}}
\author[**]{\large
{\bf Chan-Hsiang Lin}\thanks{r04943031$@$ntu.edu.tw}}
\affil[*]{Department of Computer Science and Information Engineering, \\
National Cheng Kung University, Taiwan\\
No.1, University Road, Tainan City 701, Taiwan (R.O.C.)}
\affil[**]{Department of Electrical and Electronic Engineering, \\
National Taiwan University\\
No.1, Sec. 4, Roosevelt Road, Taipei, Taiwan (R.O.C.)}
\date{}
